### 2025-08-18 Scripts/Manuscript/manuscript.Rmd
rewrote the article into complete rough draft of descriptive version

```{r helper_functions}
##### PUT THIS ALL IN A SEPARATE R SCRIPT FILE.

# Function for storing data openly in the intermediate data folder
saving_to_intermediate_data <- function(data){
  open_data(data = data, filename = paste0(paste0(
    "Data/IntermediateData/", deparse(substitute(data))), ".csv"),
    codebook = NULL, value_labels = NULL) 
}

@@

# function for changing QMP data to their ratio equivalent
Create_QMP_descriptive_case <- function(practice_name, original_coded_var, replication_coded_var){
  # add practice name to first row
  Practice <- practice_name

  # checking that we are not dividing by 0, and then calculating the ratio of 
  # QMPs for applicable items for replications
  if(N_applicable_replication != 0){
    QMP_percentage_replication <- round(replication_n_QMPs / (N_applicable_replication), 2)
  } else{
    QMP_percentage_replication <- 0
  }

@@

In psychological research we are often interested in establishing a robust effect involving one or more latent constructs (e.g., IQ and conscientiousness) that describes a psychological phenomenon (like increased conscientiousness causing a person to develop higher IQ). However in the wake of the replication crisis the robustness of effects in psychology has been called into question. The Reproducibility Project: Psychology [RPP\; @osc2015estimating] and other large-scale replication projects [@klein2014investigating; @ebersole2016many; @klein2018many; @klein2022many; @ebersole2020many] and typically yielded smaller effects in replications compared to original studies. Replicability is one of the key ways to establish the robustness of an effect (Nosek RRR & …). If an effect does not replicate, it is likely not robust. Numerous factors have been proposed to explain why the original effects did not appear robust, including questionable research practices [@simmons2011false; @john2012measuring; @cumming2014new; @wicherts2016degrees], questionable reporting practices [@bakker2011mis; @nuijten2016prevalence], biased publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science], and more.

These replication efforts and the subsequent lines of research have been of instrumental value in determining the lack of robustness in effects, uncovering what the causes of this lack of robustness are, and spearheading initiatives like … to help improve the robustness of effects. However, robustness was only one aspect of the goal highlighted at the beginning of this article, the other aspect, the fact that the effect should describe a true psychological phenomenon has received relatively less attention, although this is changing (SOME CITATIONS).

In this article, we contribute to the rising research investigating the soundness of measurement in research. After all, a true psychological phenomenon is requires accurate measurement on the relevant constructs. Our aim is to create a greater understanding of the extent to which this. We provide a descriptive account of the measurement reporting practices in the Many Labs replications and related original research, in tandem with the measure’s reliability and internal structure analyzed from the accompanying openly available data.

## Measurement Quality

To understand a psychological phenomenon you need to be able to accurately capture the relevant constructs. While this premise underlines the core idea behind the use of measures for psychological constructs, it is difficult to guarantee in practice. In general, there are two aspects of a measurement between which we distinguish: validity and reliability. What complicates things is that there are multiple aspects to validity and multiple ways to assess these aspects of validity and reliability. So a researcher needs to know which type of assessment for validity and reliability is important for a measure, and on top of that it can be a complicated task to establish validity and reliability.

Validity is an umbrella term for many different types of validity (construct, predictive, content, internal, external, etc.) and applies to (nearly) all aspects of the research design (CITATIONs INCLUDING VAZIRE et al.). For the purposes of this research we focus on construct validity of the applied measurement, which includes the measure and some aspects of the research design involving the administration of the measure. Construct validity refers to … . It is key to (relevant for nearly all measurement to some extent, because …) … . Evaluating it requires … and …, which in practice means … and … . !!!make sure that this section highlights something about construct validity relevant for our research that most psychologists may not actively realize.!!!

Reliability estimates provide an indication of how consistent the responses on a measurement are. …something about what this consistency is over [might relate to the different types: in CTT it is the correlation between scores on two equivalent forms of the test; but we are more focused on consistency as a basic requirement for an essentially valid measure, because no reliability means no validity]. Reliability is a critical first step to obtaining credible findings. Because if the scores on a measure are not consistent with themselves, it is unlikely that any effect associated with the measure can credibly be established. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual], … test-retest … interrater … internal consistency (this in turn relates back to construct validity)…. [something about the fact that reliability is sample specific and not measurement specific in nearly all cases of us assessing it]

@@

To summarize the previous section, the measurement of a study need to be both valid and reliable to be able to assess the phenomenon of interest. However, recent research has shown that the reliability and validity can often not be discerned from the reported information. Questionable Measurement Practices (QMPs) raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs\; @john2012measuring]. QMPs range from lack of transparency and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement].

@flake2022construct documented QMPs among 100 replications and their respective original articles from the RPP [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Furthermore, auxiliary information on the number of items, the response format, the scoring of the scale, was also not reported for several measures in the RPP. Furthermore, only eight of the 40 translated scales contained validity evidence for the translated version of the scale. Evidence showing that this and other modifications between original and replication did not invalidate the measurement was rare.

!!!Especially worrisome because @shaw2020measurement shows that when running factor analyses on the available data the structural evidence does not always show a good construct validity, so that the lack of reported validity evidence may be hiding psychometrical skeletons in the closet; Reliability something … [Hussey’s work]. !!!

Further findings by  @flake2022construct and others [@flake2017construct; @shaw2020measurement] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers. If it is not clear what items were used, how they were scored, and how they were administered, the reconstructed measure used in the replication may be assessing the relevant construct(s) differently, or even assess different construct(s). If different construct(s) are assessed, the replication may not be a test of the same phenomenon as the original. If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, the replication is hardly informative with regards to the phenomenon of interest. Given replication’s importance in cumulative knowledge gain in science, this is worrisome.

@@

Our aim is to further investigate the reliability, validity, and measurement reporting practices in the Many Labs replications and related original research. We provide a descriptive account of the measurement reporting practices in tandem with the measure’s reliability and validity evidence, obtained from the openly available data from the Many Labs replication projects.

Existing literature has looked at reported reliability, validity, and general measurement features in both original and replication studies before. Previous studies have also recalculated reliabilities from reported information and reanalyzed the validity from original data. Our research provides a unique contribution by combining the reported measurement information in original and replication studies, with reliability and validity re-analyses performed on openly available data from those replication studies, with the added benefit of having data across multiple labs so that variation in reliability and validity across multiple instances can be investigated.

@@

## Data Source
The data source is the Many Labs replication projects. These were a series of high profile replication projects wherein multiple psychological studies considered relevant by the community were chosen to be replicated across multiple labs over the world. Practices encountered with measurement in this sample of original articles and replications are a representative reflection of these practices more broadly.

Furthermore, because each study was replicated across multiple labs and the data collected from each lab is publicly available, we can calculate reliability coefficients and perform factor analyses for each measurement across multiple data points and investigate the variance in these estimates.

## Unit of Analysis
Our unit of analysis is a measure of a single psychological construct within a replication protocol/article. Multiple psychological constructs could be measured per original study or replication. We used the replication protocols to identify these measures. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.

## Data Collection
The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] from their respective OSF pages. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures. We checked the Many Labs data source prior to registering our coding protocol, to check the feasibility of which data could be extracted and how. However, the actual coding took place after registering the coding protocol … Further details can be found in supplement XXX.

### Replication Datasets
The replication datasets refer to the publicly available datasets containing the data obtained from all labs partaking in a Many Labs study. For the analyses, we extracted the scores on the items of each previously identified measure that met our inclusion criteria specified below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in our reliability recalculations and factor analysis checks, the measure had to be a scale consisting of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria and the nature of the available format(s) of each dataset resulted in suitable item score data from 19 replication sets spread across on average approximately 35 lab locations for our analyses.

@@

### Replication Protocols
The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the data retrieval information supplementary document; URL https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd).

### Original Articles
We identified and retrieved all original study articles using the citations for these articles in each replication protocol.

```{r CleaningCodedData, include = FALSE, eval = FALSE}
##### This code can be used to rerun the data preparation to convert the raw 
##### (input) data of the coded data into intermediate data. However, because 
##### the intermediate data is also available in this project, the manuscript  
##### can also be reproduced without running this code block.
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_sel <- coded_data_vignette_raw[3:160, 2]

@@

# fixing some coding mistakes
coded_data_full$variable_name[79] <- "quote attribution effect"
coded_data_full$N[3] <- "5284"
coded_data_full$N[158] <- "1202"
coded_data_full$reliability_type[50] <- "Not Reported"
coded_data_full$reliability_type[127] <- "Not Reported"
coded_data_full$op_1[145] <- "False"
coded_data_full$op_3[121] <- "True"
coded_data_full$op_5[157] <- "True"
coded_data_full$sel_1[59] <- "True"
coded_data_full$quant_2[113] <- "True"
coded_data_full$mod_time[1] <- "Before"

@@

## Measures
### Coding Protocol
We developed a coding protocol to extract reported measurement information from the original articles and replication protocols. We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present. Similarly, we coded if any construct validity evidence, such as a factor analysis, was presented alongside the measure. We additionally included twenty items that were based on the QMP table presented in Flake & Fried. These items recorded whether or not certain information was reported and were all coded to be either true, false, or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). Example items can been in Table 1.

@@

After the initial coding, we made minor revisions to 14 of the 20 QMP items in the preregistered coding protocol, because we considered them overly stringent in practice. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol, the results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in Supplementary Analyses D.

We initially intended to form a QMP index using these QMP items and explore relations in the data using this index, but this index could not be validated properly (more information on the index can be found in the Supplement). These items are therefore currently used on their own to give a descriptive overview of the reporting practices in our sample.

```{r Calculating_QMP_Data, include = FALSE, eval = FALSE}
original_QMP_data <- coded_data_original[c("def_1", "sel_2", "op_4", "reliability_type", "sel_existing", "op_version", "op_1_REV", "sel_1_REV", "sel_3_REV", "sel_4", "sel_psychometric_evidence", "op_2_REV", "op_3", "quant_1_REV", "quant_2_REV", "quant_3_REV", "quant_4", "op_5_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", "mod_4_REV", "mod_5_REV", "mod_6_REV")]

@@

QMP_data$reliability_reported_rep <- ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), FALSE, ifelse(replication_QMP_data$reliability_type == "Not Reported", TRUE, NA))

@@

QMP_data$source_org <- original_QMP_data$sel_1_REV
QMP_data$source_rep <- replication_QMP_data$sel_1_REV

QMP_data$select_or_create_clarity_org <- original_QMP_data$sel_existing == "Not Clearly Stated"
QMP_data$select_or_create_clarity_rep <- replication_QMP_data$sel_existing == "Not Clearly Stated"

QMP_data$version_clarity_org <- original_QMP_data$op_1_REV == FALSE | original_QMP_data$op_version == "" & original_QMP_data$sel_existing == "True, namely"
QMP_data$version_clarity_rep <- replication_QMP_data$op_1_REV == FALSE | replication_QMP_data$op_version == "" & replication_QMP_data$sel_existing == "True, namely"

@@

Recalculating Data
We furthermore, used the replication datasets to calculate reliability for each measure with appropriate data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis. Then combining these two values we conducted a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis (Botella & Suero, 2012; López-Ibáñez et al., 2024; Vacha-Haase, 1998). This enabled us to quantify the degree of true variation (or heterogeneity) in reliability coefficients across lab locations. We performed the RG meta-analysis using the rma function from the metafor R package (v4.4-0 ; Viechtbauer, 2010) and default settings. We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because Cronbach’s Alpha is used more commonly in research allowing us to make comparisons between calculated and reported reliabilities.  Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis. However, we additionally estimated McDonald’s Omega, since it has been argued to be a more informative measure of reliability than alpha, while also simultaneously providing some validity evidence [@crutzen2017scale; @deng2017testing]. Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1.

Finally, We probed the three assumptions of Cronbach’s alpha for our included nineteen measures. First, we tested for unidimensionality using the fit indices of a one-dimensional Confirmatory Factor Analysis (CFA), and the outcome from a parallel test. !!! explain parallel test !!! . Second, we compared the unidimensional model to a unidimensional model that was restricted to be Tau equivalent (equal loading of all items on the common factor), and used model comparison to test whether the restricted model fitted significantly worse or not. Third, for the unidimensional model, we tested the assumption of uncorrelated errors by freely estimated the five highest correlations between individual item pairs and then used a model comparison to test whether the model with freely estimated errors fitted significantly better or not. Besides testing the assumptions for Cronbach’s alpha, the results regarding unidimensionality combined with McDonald’s Omega also gives us some indication of the construct validity, since these measures were checked to all have been used to create a singular index. If a unidimensional model would thus lack fit according to our tests, it would put into question the use of these measures to estimate a singular variable of interest.

@@

# Results
## Reliability & Validity reporting
Figure 1 depicts the flow of measures in relation to reliability reporting. First, it shows that almost half of the measures in both replication (N = 37) and original research (N = 35) were single-item measures. Only thirteen measures in original and four in replications were reported with a reliability indicator. Cronbach’s Alpha was the most commonly reported reliability indicator.

Validity evidence was even less common than reliability evidence. Only, `r sum(coded_data_original$sel_psychometric_evidence_REV != "None" & coded_data_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_original$sel_3_REV == TRUE, na.rm = TRUE)` original studies and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)" | coded_data_replications$sel_3_REV == TRUE, na.rm = TRUE)` replications reported psychometric evidence on the . Most commonly exploratory factor analyses or convergent validity information were presented. Only `r sum(coded_data_original$sel_4 == TRUE, na.rm = TRUE)` original studies & `r sum(coded_data_replications$sel_4 == TRUE, na.rm = TRUE)` replications reported psychometric validity evidence from previous studies.

```{r code on the reporting of validity evidence}
table(coded_data_original$sel_psychometric_evidence_REV)
table(coded_data_replications$sel_psychometric_evidence_REV)

>>>>

```{r helper_functions}
# Function for storing data openly in the intermediate data folder
saving_to_intermediate_data <- function(data){
  open_data(data = data, filename = paste0(paste0(
    "Data/IntermediateData/", deparse(substitute(data))), ".csv"),
    codebook = NULL, value_labels = NULL) 
}

@@

@@

The challenge with measurement in quantitative psychological research is that psychological constructs cannot be directly measured like height or weight. Instead, we use scores from a measurement as a proxy indicator for that psychological construct. However, we cannot simply assume that any measure we create will form a good indicator of the construct. We have to substantiate this. Psychometrics can be used to statistically estimate properties of the measure that are indicative of its validity. The effort of validating a measure represents a research effort all on its own. Regardless, the burden of validating a measure – besides some well-established psychiatric and personality measures – is most often placed on the researcher using a measure as part of their broader aim to study a psychological phenomena. When the effort involved in validating a measure is relegated to being only a component of a study that is more focused on the testing of a phenomena, we have to wonder, how well does this measurement validation process go?

## Measurement Validation

When we validate a measure using psychometrics, we evaluate it mainly on two aspects: construct validity & reliability. Construct validity refers to whether the variance in the measured item scores between participants can be attributed to variance in the unobserved constructs of interest between participants (Cronbach & Meehl, 1955; Vazire et al., 2022). Whereas reliability refers to how consistent a participant's responses on a measurement are [@nunnally1978overview; @mellenbergh2011conceptual]. Reliability is part of the validation of a measure because an unreliable measure cannot consistently capture a construct through the items, and therefore cannot be assumed to properly capture the construct of interest (Crutzen & Ygram Peters, 2015). Suppose we have a measure and we want it to measure general intelligence, and we want to validate this as a measure of general intelligence. We would see our measurement as construct valid if being more intelligent resulted in generally scoring higher on our test, and our measurement would be reliable if the score of people on our measure consistently reflected their actual intelligence.

In practice construct validity is often evaluated through factor analysis. In factor analysis, a model is fitted to explain as much of the variance of multiple items through a smaller number of factors, which are each weighted averages of the item scores. The number of factors are first specified, and then the fit of a model involving those number of factors is determined. Preferably, a model with the number of factors corresponding to the number of constructs of interest should show adequate fit. Additionally, the items aimed at the same construct should be statistically related to the same factor. For example, suppose items 1 through 5 from our general intelligence measure are meant to capture verbal intelligence, and items 6 through 10 are distinctly about mathematical intelligence. To establish construct validity, we want to find that a two factor model shows adequate fit, with one factor to which items 1 through 5 relate, and one to which items 6 through 10 relate. However, even in this scenario we cannot be certain that the second factor relates to mathematical intelligence and not for example abstract thinking, other types of validity checks as well as theoretical underpinnings will be necessary. Additionally, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance (Horn et al., 1983; Cheung & Rebecca, 2012).

Reliability gives us an indication of how much our measure captures the signal of our measured variables over noise. Psychometrics offers various ways to assess reliability empirically [@nunnally1978overview; @mellenbergh2011conceptual]. For example, we can compare scores on multiple equivalent forms of the test, between multiple different raters, or between multiple different timepoints of the same test. Still, the most common way to assess reliability is through an indication of consistency within the measure itself, and the most common among these indicators is the Cronbach's Alpha coefficient. The Cronbach's Alpha coefficient is defined as “the average of all the possible split-half coefficients for a given test” (Cronbach, 1951). Here split-half coefficients being the correlation between two halves of the same test. It can be calculated by taking the ratio of interitem covariance to total variance and multiplying it by n / (n - 1), where n is the number of items in the scale. However, Cronbach's Alpha comes with strong assumptions on the underlying factor structure, including that the measure is unidimensional, so a single factor. Furthermore, because Cronbach's alpha is proportional to the total variance in the target variable in the sample, it is an indicator of reliability of a measurement, and not the measure itself. In spite of this many researchers report and interpret Cronbach's Alpha as such (Cortina, 1993; Schmitt, 1996).

Thus, psychometric tests are useful but they are not always easy to perform in practice. Even simple factor analysis requires sample sizes of at least around 100, unless the amount of variance explained by the factors is large and the factor structure is clear (Gorsuch, 1983; MacCallum et al., 1999). However, even in the latter case factor analysis does not converge with low sample sizes. Furthermore, if we want to know not just the reliability and validity of one measurement but for the measure across multiple contexts, we need to conduct multiple studies with approximately 400 people per group to detect meaningful effects (Meade & Bauer, 2007; French & Finch, 2016; Koziol & Bovaird, 2018). However, what we observe in the literature is that most measures are reused once or never (THE NOT HUSSEY PAPER ABOUT TOOTHBRUSH MEASURES; also the other Hussey paper with the blocks). Finally, \@shaw2020measurement checked the factor structure and reliability of measures used in the Many Labs 2 replication project [@klein2018many] on the available data, the results. They observed that for none of the scales they assessed, a factor structure congruent with the use of the scales met all of their evaluation criteria, and reliability was rarely consistently above an acceptable threshold.

@@

As illustrated in the previous section, validating measurement is a complex but essential part of doing psychological research. Yet the scientific community has not fully stepped up to this challenge (FLAKE & FRIED 2020). A large number of measures used in the psychological literature lack information on the validity and reliability of the measure (Hogan & Agnello, 2004; Flake et al., 2017; Flake et al., 2022).

Questionable Measurement Practices (QMPs) are practices that raise doubts about a measurement’s validity [@flake2020measurement] and have been coined as a term analogous to Questionable Research Practices [QRPs; @simmons2011false; @john2012measuring; @wicherts2016degrees]. QMPs range from lack of transparency in the reporting of the measure and unclear motivation in choice of measure to poor justification for modifications of a measure and procedure of an existing measure [@flake2020measurement]. @flake2022construct documented QMPs among 100 replications and their respective original articles from the Reproduciiblity Project Psychology [@osc2015estimating]. They coded the number of measures, the number of items in the measure, and the information that was reported describing the measure and justifying its use. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. But reporting of reliability and validity evidence is not only low, but may also be biased as well. !!!HUSSEY et al., 2023/2025!!! observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and low reporting just below .70. Thus the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

Further findings by @flake2022construct and others [@flake2017construct; @shaw2020measurement] also show that QMPs not only limit the reported validity of a measurement in a study, the lack of information also creates challenges for replicating researchers. Basic content descriptions such as the number of items, the response format, the scoring of the scale were irregular (exact numbers). If it is not clear what items were used, how they were scored, and how they were administered, then it is challenging to reconstruct the measurement for a replication study. In turn, the replication may assess the constructs in a substantially similar way, or they even assess different constructs. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. If constructs are assessed differently, the estimated effects in the replication cannot easily be substantially compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

@@

Our aim is to provide a descriptive account of the reliability, validity, and reporting practices of measurement in replications and related original research. We coded several aspects of the measurement reporting practices in replications and original articles. Additionally, we estimated the reliability and validity evidence using openly available replication data of the measurement item responses from across multiple labs. Our unique contribution is by evaluating reported and the recalculated measurement information for each measure together. This allows us to capture a "double whammy" scenario where there is uncertainty in the reliability and validity of these measures when we calculate these ourselves, and where QMPs obscure the ability to evaluate the measure as well as inhibiting future researchers to recreate the measurement to validate it in a new study. Besides this, our study also functions as a conceptual replication of earlier research looking at reporting practices and measurement validation using different questions and analyses on a different set of replications and original research. While the theory underlying the measurement is important to evaluate how the content of the measure fits to the constructs of interest, because evaluating the theory of a measurement requires domain specific knowledge for each measure we do not address it in this study, we refer interested readers to articles discussing theory in measurement elsewhere (Gehlbach & Brinkworth, 2011; Humphry, 2017; Borgstede and Eggert, 2023; Hasselman, 2023).

@@

## Data Source

The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@klein2014investigating; @ebersole2016many; @klein2018many; @ebersole2020many] from their respective OSF pages. Many Labs 4 [@klein2022many] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

## Unit of Analysis

Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated. We allowed for multiple variables to be measured per study. We used the replication protocols to identify the measure of each variable. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses.

## Data Collection

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the coding protocol information file in the supplementary materials.

### Replication Datasets

The replication datasets refer to the publicly available datasets containing the data obtained from all labs of a Many Labs replication. For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data\$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data\$g)), 0)` lab locations for our analyses.

@@

### Replication Protocols

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the data retrieval information XXX supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

### Original Articles

We identified and retrieved all original study articles using the citations for these articles in each replication protocol.

```{r CleaningCodedData, include = FALSE, eval = FALSE}
##### This code can be used to rerun the data preparation to convert the raw 
##### (input) data of the coded data into intermediate data. However, because 
##### the intermediate data is also available in this project, the manuscript  
##### can also be reproduced without running this code block.

# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_sel <- coded_data_vignette_raw[3:160, 2]

@@

# fixing some coding mistakes
coded_data_full$variable_name[79] <- "quote attribution effect"
coded_data_full$N[3] <- "5284"
coded_data_full$N[158] <- "1202"
coded_data_full$reliability_type[50] <- "Not Reported"
coded_data_full$reliability_type[127] <- "Not Reported"
coded_data_full$op_1[145] <- "False"
coded_data_full$op_3[121] <- "True"
coded_data_full$op_5[157] <- "True"
coded_data_full$sel_1[59] <- "True"
coded_data_full$quant_2[113] <- "True"
coded_data_full$mod_time[1] <- "Before"
coded_data_full$psychometric_evidence_text_REV[coded_data_full$sel_psychometric_evidence_text_REV == "convergent validitiy"] <- "convergent validity"

@@

## Measures

### Coding Protocol

We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol. We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present. Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure. We additionally included twenty items that were based on the QMP table presented in Flake & Fried (2020). For each of these items we a piece information we would want to see reported with regards to the measurement was described. If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). Example items can be seen in Table 1.

@@

After the initial coding, we made minor revisions to 14 of the 20 QMP items from the preregistered coding protocol. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The results of the equivalent analyses based on QMPs obtained with our initial protocol can be found in Supplementary Analyses D.

We initially intended to form a QMP index using these QMP items and perform regression analyses using this index, but this index could not be validated properly and its results would be misleading to present here. A more detailed explanation of what was omitted and why, as well as the results from the preregistered analyses themselves can be found in Supplementary Materials XXX. The items are currently used as individual descriptives on the reporting practices in our sample.

```{r Calculating_QMP_Data, include = FALSE, eval = FALSE}
# function for changing QMP data to their ratio equivalent
Create_QMP_descriptive_case <- function(practice_name, original_coded_var, replication_coded_var){
  # add practice name to first row
  Practice <- practice_name

  # checking that we are not dividing by 0, and then calculating the ratio of 
  # QMPs for applicable items for replications
  if(N_applicable_replication != 0){
    QMP_percentage_replication <- round(replication_n_QMPs / N_applicable_replication, 2)
  } else{
    QMP_percentage_replication <- 0
  }

# loading the relevant items
original_QMP_data <- coded_data_original[c("def_1", "sel_2", "op_4", "reliability_type", "sel_existing", "op_version", "op_1_REV", "sel_1_REV", "sel_3_REV", "sel_4", "sel_psychometric_evidence", "op_2_REV", "op_3", "quant_1_REV", "quant_2_REV", "quant_3_REV", "quant_4", "op_5_REV", "mod_1_REV", "mod_2_REV", "mod_3_REV", "mod_4_REV", "mod_5_REV", "mod_6_REV")]

@@

QMP_data$reliability_reported_rep <- ifelse(replication_QMP_data$reliability_type != "Not Reported" & replication_QMP_data$reliability_type != "" & !is.na(replication_QMP_data$reliability_type), TRUE, ifelse(replication_QMP_data$reliability_type == "Not Reported", FALSE, NA))

@@

@@

### Recalculating Data

We calculated reliability for each measure from the replication datasets with suitable data for each lab the measure was used in. We calculated both Cronbach’s alpha, as well as its standard error using formulas 2 & 3 from Duhachek and Lacobucci (2004) to calculate the standard error in the meta-analysis. Then we entered these two values into a meta-analysis of the reliability, also commonly referred to as a Reliability Generalization (RG) Meta-Analysis (Botella & Suero, 2012; López-Ibáñez et al., 2024; Vacha-Haase, 1998). Using RG Meta-Analysis we quantified the degree of true variation (or heterogeneity) in reliability coefficients across lab locations. We performed the RG Meta-Analysis using the rma function from the metafor R package (v4.4-0; Viechtbauer, 2010) and default settings. We evaluated the heterogeneity using the tau statistic and the Cochran's Q-test (CITATION Cochran 1954). These indicators have received criticism as indicators of heterogeneity, especially when within study sample sizes are small and power to detect heterogeneity is low (Hoaglin 2015; Pereira et al. 2010). Therefore, we also present the prediction interval and suggest that the heterogeneity results should be viewed with a critical eye (Borenstein 2024 CITATION). We implemented no correction for bias, because the Many Labs replications were not at risk of publication bias.

Our analyses will focus on Cronbach’s Alpha, because its common use in research allows us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the RG meta-analysis. We additionally estimated McDonald’s Omega for each lab from the same set of replications as for Cronbach's Alpha, since it has been argued to be a more informative measure of reliability than Cronbach's Alpha, while also simultaneously providing some validity evidence [@crutzen2017scale; @deng2017testing]. McDonald’s Omega was calculated using the omega function in the *psych* R package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1. No RG Meta-Analysis was performed on McDonald's Omega, as we could not find a formula for calculating its standard error.

@@

Finally, we also tested these measures for unidimensionality. Our unidimensionality check serves a double purpose. First, unidimensionality is one of the assumptions of Cronbach's Alpha. If this assumption does not hold for a measure, Cronbach's Alpha gives a biased and uninformative estimate of the reliability. Second, all measurement items for which unidimensionality was checked, were used to form a singular index of one latent vasriable. Certainly, not all singular indexes require the underlying latent factor model to be unidimensional (e.g., general intelligence can be used as a variable on its own or sub-divided in multiple components such as numerical and verbal intelligence). Still, we believe it is not unreasonable to assume that for most of our measures we should observe a unidimensional factor model to have at least adequate fit.

We tested for unidimensionality using two tests on the data from each lab for each measure. If at least one of these tests was passed, the measure in that lab was marked as unidimensional. For the first test we fit a Confirmatory Factor Analysis (CFA) model with one factor to the data, and we then evaluate the RMSEA value. If this value is below .08, the test is passed. For the second test we run a parallel analysis. This runs multiple Exploratory Factor Analyses (EFA) where the number of factors in the model is increased by 1 until the number of factors is one less than the number of items. It then compares the eigenvalues (an indication of how much variance is explained by that factor) of each factor to the eigenvalues for that factor if the data matrix was effectively random. If only the single factor has an eigenvalue that is significantly higher than the eigenvalue when the data matrix is random, the test is passed. We chose a combination of these two tests, as the RMSEA is known to be biased for models with small degrees of freedom (Kenny et al., 2015), while the parallel analysis may be less suited if a two or more factor solution would also fit the sample item data.
